---
title: "1001-map"
author: "Mac Campbell"
date: "August 3, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse)
library(ggrepel)
library(maps)
library(mapdata)
library(maptools)
library(rgdal)
library(raster)
library(ggsn)
```

## Get range maps from PISCES
```{r}
x<--122.293309
y<-40.804313
type<-as_tibble(cbind(x,y))

range<-getKMLcoordinates("outputs/1000/histrange.kml", ignoreAltitude=TRUE)

#Gives a list of six.... Would be nice to have a convex hull.
#This doesn't seem like a smart way to do it, but oh well.
df1<-as_tibble(range[[1]])
df2<-as_tibble(range[[2]])
df3<-as_tibble(range[[3]])
df4<-as_tibble(range[[4]])
df5<-as_tibble(range[[5]])
df6<-as_tibble(range[[6]])

#using a convex hull looks bad : (
#mrrtrange<-df[chull(c(df$V1,df$V2)),]

#Combining polygons and then getting coords for a label
df<-rbind(df1,df2,df3,df4,df5,df6)

x2<-mean(df$V1)
y2<-mean(df$V2)
curated<-as_tibble(cbind(x2,y2))

map1<-ggplot() + 
  geom_polygon(data=df1,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_polygon(data=df2,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_polygon(data=df3,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_polygon(data=df4,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_polygon(data=df5,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_polygon(data=df6,aes(x=V1, y=V2), alpha=0.75, fill="red") +
  geom_point(data=type, aes(x=x, y=y))+
  geom_label_repel(data=type, aes(x=x, y=y, label="shastae and stonei \n type locality"), alpha=0.75)+
  geom_label_repel(data=curated, aes(x=x2, y=y2, label="Historic Range of McCloud Redband Trout"), alpha=0.75)+
  coord_fixed(ratio=1.3)+
  theme_bw() +
  theme(panel.grid=element_blank())+
  xlab("Longitude")+
  ylab("Latitude")

map1
```

## We want some more native trouts

```{r}
aquilarum<-getKMLcoordinates("outputs/1000/aquilarum.kml", ignoreAltitude=TRUE)
#7 polys

range<-aquilarum
df1<-as_tibble(range[[1]])
df2<-as_tibble(range[[2]])
df3<-as_tibble(range[[3]])
df4<-as_tibble(range[[4]])
df5<-as_tibble(range[[5]])
df6<-as_tibble(range[[6]])
df7<-as_tibble(range[[7]])

df<-rbind(df1,df2,df3,df4,df5,df6,df7)

x2<-mean(df1$V1)
y2<-mean(df$V2)
curated<-as_tibble(cbind(x2,y2))

map2<- map1 + 
  geom_polygon(data=df1,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df2,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df3,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df4,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df5,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df6,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_polygon(data=df7,aes(x=V1, y=V2), alpha=0.75, fill="orange") +
  geom_label_repel(data=curated, aes(x=x2, y=y2, label="Historic Range of Eagle Lake Trout"), alpha=0.75)


map2
```

```{r}
#aguabonita<-getKMLcoordinates("outputs/1000/aguabonita.kml", ignoreAltitude=TRUE)
#Wow, 20 polygons, really should work with *.shp
aguabonita<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM14_16/f_SOM14_16.shp","f_SOM14_16")

#It is projected
#+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80
#+towgs84=0,0,0,0,0,0,0 +units=m +no_defs 

aguaWGS <- spTransform(aguabonita, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
agua<-fortify(aguaWGS)

ggplot() + geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="red")

map2+geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="red")
```

#Getting all the shapefiles

```{r}
mccloud<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM10_16/","f_SOM10_16")
mccloud <- spTransform(mccloud, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
mccloud<-fortify(mccloud)

eagle<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM12_16/","f_SOM12_16")
eagle <- spTransform(eagle, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
eagle<-fortify(eagle)

goose<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM11_16/","f_SOM11_16")
goose <- spTransform(goose, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
goose<-fortify(goose)

kern<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM15_16/","f_SOM15_16")
kern <- spTransform(kern, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
kern<-fortify(kern)

krrb<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM13_16/","f_SOM13_16")
krrb <- spTransform(krrb, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
krrb<-fortify(krrb)

crt<-readOGR("/Users/mac/github/mccloud-rrt/outputs/1000/f_SOM09_16/","f_SOM09_16")
crt <- spTransform(crt, CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
crt<-fortify(crt)

#warner
load("outputs/1000/warner.RData")

##Convex hull crt?
ccrt<-crt[chull(x=crt$long,y=crt$lat),] %>% mutate(order=1:n()) %>% mutate(group=1)
ggplot() + geom_polygon(data=ccrt, aes(x=long, y=lat, group=group))

library("concaveman")
cavecrt<-as_tibble(concaveman(as.matrix(cbind(ccrt$long, ccrt$lat)), concavity = 2)) %>%
  rename(long=V1, lat=V2) %>% mutate(order=1:n(), group=1)
ggplot() + geom_polygon(data=cavecrt, aes(x=long, y=lat, group=group))
## Look to be roughly the same

ggplot() + 
  geom_polygon(data=ccrt, aes(x=long, y=lat, group=group), fill="skyblue", alpha=0.75) +
  geom_polygon(data=mccloud,aes(x=long, y=lat, group=group), fill="red", alpha=0.75) +
  geom_polygon(data=goose,aes(x=long, y=lat, group=group), fill="pink", alpha=0.75) +
  geom_polygon(data=warner,aes(x=long, y=lat, group=group), fill="darkred", alpha=0.75) +
  geom_polygon(data=eagle, aes(x=long, y=lat, group=group), fill="brown", alpha=0.75) +
  geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="goldenrod", alpha=0.75) +
  geom_polygon(data=kern,aes(x=long, y=lat, group=group), fill="yellow", alpha=0.75) +
  geom_polygon(data=krrb,aes(x=long, y=lat, group=group), fill="gold", alpha=0.75) +
  coord_fixed(ratio=1.3)+
  theme_bw() +
  theme(panel.grid=element_blank())+
  xlab("Longitude")+
  ylab("Latitude")

```

##Raster
And the state map
```{r}

states<-map_data("state") %>% filter(region %in% c("california","oregon","nevada"))

cali<- map_data("state") %>% filter(region %in% c("california"))
domain <- c(min(states$long), max(states$long), min(states$lat), max(states$lat))

# here eric implements something and I copy it
tidy_subset <- function(x, longlat) {
  x@data$id <- rownames(x@data)
  x.f <- broom::tidy(x) %>%
    dplyr::left_join(., x@data, by = "id") %>%
    dplyr::tbl_df() %>%
    filter(long > longlat[1],
           long < longlat[2],
           lat > longlat[3],
           lat < longlat[4])
}


earth<-stack("~/github/yosemite-toad/data/HYP_HR_SR/HYP_HR_SR.tif")
earthc<-crop(earth, y=extent(domain))

rast.table <- data.frame(xyFromCell(earthc, 1:ncell(earthc)),
                         getValues(earthc/255))

rast.table$rgb <- rgb(rast.table$HYP_HR_SR.1, rast.table$HYP_HR_SR.2, rast.table$HYP_HR_SR.3)

lakes<-readOGR("outputs/1000/ne_10m_lakes")
#lakes<-fortify(lakes)
lakes<-tidy_subset(lakes, domain)

rivers<-readOGR("outputs/1000/ne_10m_rivers_lake_centerlines/")
#rivers<-fortify(rivers)
rivers<-tidy_subset(rivers, domain)

coast<-readOGR("outputs/1000/ne_10m_coastline")
#coast<-fortify(coast)
coast<-tidy_subset(coast, domain)

oceans<-readOGR("outputs/1000/ne_10m_ocean/")
oceansdf<-fortify(oceans)
oceanssub<-tidy_subset(oceans, domain)

ggplot()+
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
 # geom_polygon(data=oceans,  aes(x=long, y=lat, group=group), fill="blue", alpha=0.25) +
  geom_polygon(data=lakes, aes(x=long, y=lat, group=group), fill="blue", alpha=0.5) +
  geom_path(data=coast, aes(x=long, y=lat, group=group), color="black", alpha=0.75) +
  geom_path(data=rivers,aes(x=long, y=lat, group=group), color="blue", alpha=0.5) + 
  coord_fixed(ratio=1.3, xlim = c(min(cali$long), max(cali$long)), ylim=c(min(cali$lat), max(cali$lat)))


```



##Putting it all together
```{r,eval=FALSE}
ggplot()+
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
  geom_polygon(data=states, aes(x=long, y=lat, group=group), color="black", alpha=0, fill="white")+
  geom_polygon(data=lakes, aes(x=long, y=lat, group=group), fill="blue", alpha=0.5) +
#  geom_path(data=coast, aes(x=long, y=lat, group=group), color="black", alpha=0.75) +
  geom_path(data=rivers,aes(x=long, y=lat, group=group), color="blue", alpha=0.5) + 
  geom_polygon(data=crt, aes(x=long, y=lat, group=group), fill="grey50", alpha=0.75) +
  geom_polygon(data=mccloud,aes(x=long, y=lat, group=group), fill="red", alpha=0.75) +
  geom_polygon(data=goose,aes(x=long, y=lat, group=group), fill="pink", alpha=0.75) +
  geom_polygon(data=eagle, aes(x=long, y=lat, group=group), fill="brown", alpha=0.75) +
  geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="goldenrod", alpha=0.75) +
  geom_polygon(data=kern,aes(x=long, y=lat, group=group), fill="yellow", alpha=0.75) +
  geom_polygon(data=krrb,aes(x=long, y=lat, group=group), fill="gold", alpha=0.75) +
  geom_point(data=type, aes(x=x, y=y)) +
  geom_label_repel(data=type, aes(x=x, y=y, label="shastae and stonei \n type locality"),
                   size=3, alpha=0.75)+
  coord_fixed(ratio=1.3, xlim = c(min(cali$long), -116), ylim=c(34, max(cali$lat))) +
  theme_bw() +
  theme(panel.grid=element_blank())+
  xlab("Longitude")+
  ylab("Latitude")


```

I think the map needs....

1. McCloud River
2. Golden Trout rivers, or at least the Kern
3. Bay filled in.
4. Oceans.

Getting a bit more detailed map.
https://www.naturalearthdata.com/downloads/10m-raster-data/10m-natural-earth-2/
```{r}

nat.earth<-stack("~/github/mccloud-rrt/outputs/1000/NE2_HR_LC_SR_W_DR/NE2_HR_LC_SR_W_DR.tif")

nat.crop <- crop(nat.earth, y=extent(domain))

rast.table <- data.frame(xyFromCell(nat.crop, 1:ncell(nat.crop)),
                         getValues(nat.crop/255))


rast.table$rgb <- with(rast.table, rgb(NE2_HR_LC_SR_W_DR.1,
                                       NE2_HR_LC_SR_W_DR.2,
                                       NE2_HR_LC_SR_W_DR.3,
                                       1))
```

```{r}
ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) 

```

Oooh, that looks good.

```{r}
ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
  geom_polygon(data=states, aes(x=long, y=lat, group=group), color="black", alpha=0, fill="white") +
#  geom_polygon(data=crt, aes(x=long, y=lat, group=group), fill="grey50", alpha=0.75) +
  geom_polygon(data=mccloud,aes(x=long, y=lat, group=group), fill="red", alpha=0.75) +
  geom_polygon(data=goose,aes(x=long, y=lat, group=group), fill="pink", alpha=0.75) +
  geom_polygon(data=eagle, aes(x=long, y=lat, group=group), fill="brown", alpha=0.75) +
  geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="goldenrod", alpha=0.75) +
  geom_polygon(data=kern,aes(x=long, y=lat, group=group), fill="yellow", alpha=0.75) +
  geom_polygon(data=krrb,aes(x=long, y=lat, group=group), fill="gold", alpha=0.75) +
  geom_point(data=type, aes(x=x, y=y)) +
  geom_label_repel(data=type, aes(x=x, y=y, label="shastae and stonei \n type locality"),
                   size=3, alpha=0.75)+
  coord_fixed(ratio=1.3, xlim = c(min(cali$long), -116), ylim=c(34, max(cali$lat))) +
  theme_bw() +
  theme(panel.grid=element_blank())+
  xlab("Longitude")+
  ylab("Latitude")


```


Make some labels for the polygons

```{r}
longs<-c(type$x, -122.024996, mean(mccloud$long), mean(goose$long), mean(eagle$long), mean(agua$long), mean(kern$long), mean(krrb$long))
lats<-c(type$y, 41.241416, mean(mccloud$lat), mean(goose$lat), mean(eagle$lat), mean(agua$lat), mean(kern$lat), mean(krrb$lat) )
labels<-c("Type locality of \n shasta and stonei","McCloud Falls","McCloud Redband", "O. m. sp. 'Goose Lake'", "O. m. aquilarum", "O. m. aquabonita", "O. m. whitei", "O. m. gilberti")

text<-tibble(longs, lats, labels)

ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
  geom_polygon(data=states, aes(x=long, y=lat, group=group), color="black", alpha=0, fill="white") +
#  geom_polygon(data=crt, aes(x=long, y=lat, group=group), fill="grey50", alpha=0.75) +
  geom_polygon(data=mccloud,aes(x=long, y=lat, group=group), fill="red", alpha=0.75) +
  geom_polygon(data=goose,aes(x=long, y=lat, group=group), fill="pink", alpha=0.75) +
  geom_polygon(data=eagle, aes(x=long, y=lat, group=group), fill="brown", alpha=0.75) +
  geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="goldenrod", alpha=0.75) +
  geom_polygon(data=kern,aes(x=long, y=lat, group=group), fill="yellow", alpha=0.75) +
  geom_polygon(data=krrb,aes(x=long, y=lat, group=group), fill="gold", alpha=0.75) +
  geom_point(data=type, aes(x=x, y=y)) +
  geom_point(aes(x=-122.024996, y=41.241416), pch=17)+
  geom_label_repel(data=text, aes(x=longs, y=lats, label=labels), size=3, alpha=0.75)+
  coord_fixed(ratio=1.3, xlim = c(-124, -116), ylim=c(34, max(cali$lat))) +
  theme_bw() +
  theme(panel.grid=element_blank())+
  xlab("Longitude")+
  ylab("Latitude")

```

Eagle lake

```{r}
load("/Users/mac/Dropbox/trout/chinook/Chinook Paper/polyStreamsSub.rda")
lakes<- subset(polyStreamsSub, polyStreamsSub$NAME %in% c(                                                         "Eagle Lake"
                                                          
))
lakesdf<-fortify(lakes)


load("/Users/mac/Dropbox/trout/chinook/Chinook Paper/streamsSub.rda")
riversNames<-as_tibble(read.csv(file="/Users/mac/Dropbox/trout/chinook/Chinook Paper/outputs/toPlot.txt",header=T))
riversNames$Names<-as.character(riversNames$Names)

rivers<- subset(streamsSub, streamsSub$NAME %in% c("McCloud River", "Pit River"))
riversdf<-fortify(rivers)                                                     

ggplot()+
    geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
    geom_polygon(data=lakesdf, aes(x=long, y=lat, group=group), fill="#69A0C5FF", color="#69A0C5FF", alpha=0.75) +
    geom_path(data = riversdf, aes(x = long, y = lat, group=group), color="blue", alpha=0.75)


```

## Get some collection information
```{r}
points<-read_csv("~/Dropbox/Redband Trout/mac-mrrt-manuscript/trout-collections-for-plotting-pure.csv") %>%
  dplyr::select(Latitude, Longitude, `Location Code`)

colls<-points %>% unique() %>% filter(Latitude !="NA")

ggplot() +
  geom_point(data=colls, aes(x=Longitude, y=Latitude)) +
  geom_text_repel(data=colls, aes(x=Longitude, y=Latitude, label=`Location Code`))
```

##Print it out

```{r}
labels2<-c("Type locality of\nshasta and stonei","McCloud Falls", "McCloud River\nTrout","Goose Lake and Pit River\nRedband Trout",
           "Eagle Lake Rainbow Trout","California Golden Trout","Little Kern Golden Trout","Kern River Rainbow Trout")
```

```{r}
themap<-ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE) +
 # geom_polygon(data=states, aes(x=long, y=lat, group=group), color="black", alpha=0, fill="white",
 #              size=1.5) +
  geom_polygon(data=lakesdf, aes(x=long, y=lat, group=group), fill="#69A0C5FF", color="#69A0C5FF", alpha=0.75) +
  geom_path(data = riversdf, aes(x = long, y = lat, group=group), color="blue", size=1, alpha=0.75) +
  #ccrt for convex hull, crt for HUC polys
  geom_polygon(data=crt, aes(x=long, y=lat, group=group), fill="grey50", alpha=0.5) +
  geom_polygon(data=mccloud,aes(x=long, y=lat, group=group), fill="red", alpha=0.75) +
  geom_polygon(data=goose,aes(x=long, y=lat, group=group), fill="pink", alpha=0.75) +
  geom_polygon(data=warner,aes(x=long, y=lat, group=group), fill="darkred", alpha=0.75) +
  geom_polygon(data=eagle, aes(x=long, y=lat, group=group), fill="brown", alpha=0.75) +
  geom_polygon(data=agua,aes(x=long, y=lat, group=group), fill="goldenrod", alpha=0.75) +
  geom_polygon(data=kern,aes(x=long, y=lat, group=group), fill="yellow", alpha=0.75) +
  geom_polygon(data=krrb,aes(x=long, y=lat, group=group), fill="gold", alpha=0.75) +
  geom_point(data=type, aes(x=x, y=y), cex=2, pch=15) +
  geom_point(aes(x=-122.024996, y=41.241416), pch=17, cex=2)+
  geom_point(data=colls, aes(x=Longitude, y=Latitude)) +
  geom_text_repel(data=colls, aes(x=Longitude, y=Latitude, label=`Location Code`)) +
  geom_text_repel(aes(x=c(-121.507590,-122.077220,-122.337596,-122.017381), 
                      y=c(40.971201, 41.172051,  40.757050,  39.761715),
                      label=c("Pit River", "McCloud River", "Shasta Lake", "Sacramento River"))) +
  geom_label_repel(data=text, aes(x=longs, y=lats, label=labels2), size=4, alpha=0.75)+
  coord_fixed(ratio=1.3, xlim = c(-124.2, -118), ylim=c(35.25, 41.7)) +
  theme_bw() +
  theme(panel.grid=element_blank())+
  theme(axis.text = element_text(size=12)) +
  theme(axis.title = element_text(size=16)) +
  xlab("Longitude")+
  ylab("Latitude")

themap +
    scalebar(x.min = -118, x.max = -124.2,
                   y.min = 35.25, y.max = 41.87,
                   dist = 100, dist_unit = "km",
                   st.bottom = FALSE, st.color = "black",
             transform = TRUE, model = "WGS84")

ggsave("outputs/1000/draft-map.pdf", width=8.5*0.65, height=11*0.65)

```