---
title: "1300-omy20"
author: "Mac Campbell"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(viridis)
library(ggpubr)
library(grid)
library(gridExtra)
library(RColorBrewer)
library(ggrepel)
```

## Make a PCA of omy20 inversion region.

omy20:5446054-18985808     
Get omy20
(base) maccamp@farm:~/mccloud-rrt/outputs/1300$ gunzip -c ../population-genetics/318.beagle.gz | grep omy20 > omy20.beagle

8768 variants     
2915 in inversion zone     
Number of sites after MAF filtering (0.05): 1043

What does a PCA look like?   

```{sh, eval=FALSE}
srun -p high -t 1:00:00 python $HOME/pcangsd/pcangsd.py -beagle outputs/1300/omy20-inv.beagle.gz -o outputs/1300/omy20-inv -threads 10
```


```{r}
meta<-read_csv("meta/318.csv")
```

Summarize Meta

```{r}
meta %>% group_by(Group, MajorGroup) %>% summarize(Count=n()) %>% select(MajorGroup, Group, Count) %>% arrange(MajorGroup)
```

### PCA

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Some shameless copying from Eric A.
#' @param samples character vector with the individuals IDs in the order in which
#' they were passed in the bamlist to angsd.
#' @param cov covariance matrix
covar2pcs <- function(samples, cov) {
  
  
  eig <- eigen(cov, symm = TRUE)
  PC <- as.data.frame(eig$vectors) %>%
    as_tibble() %>%
    setNames(sprintf("PC-%02d", 1:ncol(.)))
  
  samtib <- tibble(sample = samples)
  
  list(
    PCs = bind_cols(samtib, PC),
    eigevalues = eig$values
  )
}
```

```{r, warning=FALSE, message=FALSE}
cov<-read_delim("outputs/1300/omy20-inv.cov", col_names=FALSE, delim=" ") %>% as.matrix()
```


```{r}
pca <- covar2pcs(meta$Bamlist, cov)

pca_long <- pca$PCs %>%
  tidyr::gather(., key = "PC", "val", -sample)

# then expand a grid of the possible comparisons (ordered)
expg <- expand.grid(sample = pca$PCs$sample,
                    PCx = sprintf("PC-%02d", 1:6),
                    PCy = sprintf("PC-%02d", 1:6),
                    stringsAsFactors = FALSE) %>%
  tibble::as_tibble()

# then left join the pca results onto that
pca_pairs <- dplyr::left_join(expg, pca_long, by = c("sample", "PCx" = "PC")) %>%
  dplyr::rename(val_x = val) %>%
  dplyr::left_join(pca_long, by = c("sample", "PCy" = "PC")) %>%
  dplyr::rename(val_y = val)

pp_meta <- pca_pairs %>%   # just keep the first 6 PCs around
  left_join(., meta, by = c("sample" = "Bamlist"))

# now, that has the first 6 PCs in it.  If we want to focus on the just the
# first 3, we could do 
npc <- 3
pp_meta2 <- pp_meta %>%
  filter( (PCx %in% sprintf("PC-%02d", 1:npc)) & 
            (PCy %in% sprintf("PC-%02d", 1:npc)) )

ggplot(pp_meta2, aes(x = val_x, y = val_y, fill = Group)) +
  geom_point(pch = 21, size = 2) +
  scale_fill_discrete(na.value = "white") + 
  facet_grid(PCy ~ PCx, scales = "free")


```


```{r}

eig <- eigen(cov, symm = TRUE)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)
```



```{r}
sub12<-pp_meta2 %>% filter( (PCx =="PC-01") & (PCy =="PC-02") )

pc12<-ggplot(sub12, aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("A") +
  theme(plot.title = element_text(face="bold", size=16))

sub13<-pp_meta2 %>% filter( (PCx =="PC-01") & (PCy =="PC-03") )

pc13<-ggplot(sub13, aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC3", " ", round((100*var[3]),2), "%", sep = ""))+
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  guides(fill = guide_legend(override.aes=list(shape=15, color= viridis(8, option="magma")))) +
  ggtitle("B") +
  theme(plot.title = element_text(face="bold", size=16))


pcs<-ggarrange(pc12, pc13, ncol = 2, widths=c(1.1, 1.4))
pcs

ggsave("outputs/1300/omy20-pcs.pdf", width=9.5, height=4.5)

```

Looks inversion-y! Low frequency of one type in Coastal Rainbow Trout groups. 

```{r}
ggplot(sub12 %>% filter(val_x < -0.12), aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  geom_text_repel(aes(label=Watershed), max.overlaps = Inf) +
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("Homozygous Fish") +
  theme(plot.title = element_text(face="bold", size=16))
```

```{r}
ggplot(sub12 %>% filter(val_x > -0.12) %>% filter(val_x < -0.04), aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  geom_text_repel(aes(label=Watershed), max.overlaps = Inf) +
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("Heterozygous Fish") +
  theme(plot.title = element_text(face="bold", size=16))
```

318 has 24 hets

```{r}
hets<-sub12 %>% filter(val_x > -0.12) %>% filter(val_x < -0.04)

write_tsv(hets %>% select(Path), "bamlists/hets318.bamlist", col_names = FALSE)
```


Call genos....

```{sh, eval=FALSE}
srun -p high -t 1:00:00 angsd -P 8 -b bamlists/hets318-edited.bamlist -minInd 43  -out outputs/1300/hets-omy20 -minMaf 0.05 -minMapQ 10 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 -doGeno 4 -doPost 1 -postCutoff 0.95 -doPlink 2 -r omy20 > outputs/1300/hets.stdout 2> outputs/1300/hets.stderr &

#calc ld, 830 sites (338 in inversion). Relaxing to 2045 sites
#Expanding to some homes/hets, 24 hets, five homs? 207 sites, relaxed to 779
#Reducing ancestral homs, 48 samples. 855sites
plink --tfam  outputs/1300/hets-omy20.tfam  --tped outputs/1300/hets-omy20.tped --r2 inter-chr --ld-window-r2 0.1 --chr omy20 --out outputs/1300/troutomy20-ld --noweb --allow-extra-chr --double-id
```


```{r}
ld<-read.delim("outputs/1300/troutomy20-ld.ld",sep="",stringsAsFactors=FALSE)
head(ld)

ld %>% ggplot()+geom_histogram(aes(x=R2))
ggsave("outputs/1300/hets-troutomy20-histo.pdf")

```
```{r}
filtered<-ld %>% filter(R2>=0.7) %>% arrange(R2)

ggplot(filtered, aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  geom_point()+
  scale_color_gradient(low="white",high="red")+
  theme_bw()

ggsave("outputs/1300/hets-troutomy20-ld.jpeg")
```

## Can expand with Columbia sampling.

```{sh, eval=FALSE}
 srun -p high -t 48:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  -bam bamlists/407.single.bamlist -minInd 366 -GL 1 -ref genome/omyV6Chr.fasta -r omy20:5446054-18985808 \
  -doGLF 2 -doMajorMinor 1 -doMaf 2 -SNP_pval 1e-6 -minMapQ 20 -minQ 20 \
  -out outputs/1300/407-inv.single > outputs/1300/beagle.out 2> outputs/1300/beagle.err &
  
srun -p high -t 1:00:00 python $HOME/pcangsd/pcangsd.py -beagle outputs/1300/407-inv.single.beagle.gz -o outputs/1300/407-inv.single -threads 10
```

	-> Number of sites retained after filtering: 1166 
  -> Number of sites after MAF filtering (0.05): 275

```{r}
meta<-read_csv("meta/combined.csv")
```


```{r, warning=FALSE, message=FALSE}
cov<-read_delim("outputs/1300/407-inv.single.cov", col_names=FALSE, delim=" ") %>% as.matrix()
```


```{r}
pca <- covar2pcs(meta$Bamlist, cov)

pca_long <- pca$PCs %>%
  tidyr::gather(., key = "PC", "val", -sample)

# then expand a grid of the possible comparisons (ordered)
expg <- expand.grid(sample = pca$PCs$sample,
                    PCx = sprintf("PC-%02d", 1:6),
                    PCy = sprintf("PC-%02d", 1:6),
                    stringsAsFactors = FALSE) %>%
  tibble::as_tibble()

# then left join the pca results onto that
pca_pairs <- dplyr::left_join(expg, pca_long, by = c("sample", "PCx" = "PC")) %>%
  dplyr::rename(val_x = val) %>%
  dplyr::left_join(pca_long, by = c("sample", "PCy" = "PC")) %>%
  dplyr::rename(val_y = val)

pp_meta <- pca_pairs %>%   # just keep the first 6 PCs around
  left_join(., meta, by = c("sample" = "Bamlist"))

# now, that has the first 6 PCs in it.  If we want to focus on the just the
# first 3, we could do 
npc <- 3
pp_meta2 <- pp_meta %>%
  filter( (PCx %in% sprintf("PC-%02d", 1:npc)) & 
            (PCy %in% sprintf("PC-%02d", 1:npc)) )

ggplot(pp_meta2, aes(x = val_x, y = val_y, fill = Group)) +
  geom_point(pch = 21, size = 2) +
  scale_fill_discrete(na.value = "white") + 
  facet_grid(PCy ~ PCx, scales = "free")


```


```{r}

eig <- eigen(cov, symm = TRUE)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)
```



```{r}
sub12<-pp_meta2 %>% filter( (PCx =="PC-01") & (PCy =="PC-02") )

pc12<-ggplot(sub12, aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("A") +
  theme(plot.title = element_text(face="bold", size=16))

sub13<-pp_meta2 %>% filter( (PCx =="PC-01") & (PCy =="PC-03") )

pc13<-ggplot(sub13, aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC3", " ", round((100*var[3]),2), "%", sep = ""))+
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  guides(fill = guide_legend(override.aes=list(shape=15, color= viridis(8, option="magma")))) +
  ggtitle("B") +
  theme(plot.title = element_text(face="bold", size=16))


pcs<-ggarrange(pc12, pc13, ncol = 2, widths=c(1.1, 1.4))
pcs

ggsave("outputs/1300/omy20-pcs-forward-only.pdf", width=9.5, height=4.5)

```

```{r}
ggplot(sub12 %>% filter(val_x < -0.12), aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  geom_text_repel(aes(label=Watershed), max.overlaps = Inf) +
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("Homozygous Fish") +
  theme(plot.title = element_text(face="bold", size=16))


ggsave("outputs/1300/omy20-pcs-forward-only-homs.jpeg")
```

Wow! Restricted to CRT from Coastal CA

```{r}
ggplot(sub12 %>% filter(val_x > -0.12) %>% filter(val_x < -0.04), aes(x = val_x, y = val_y, fill = Group, shape=MajorGroup)) +
  geom_point(size = 2, alpha=0.75) +
  scale_fill_discrete(na.value = "white") + 
  theme_bw()+
  theme(panel.grid=element_blank())+
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = ""))+
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = ""))+
  geom_text_repel(aes(label=Watershed), max.overlaps = Inf) +
  scale_fill_viridis_d(option = "magma") +
  scale_shape_manual("Major Group", values = c(21,22,22,23,24,25)) +
  theme(legend.position = "")+
  ggtitle("Heterozygous Fish") +
  theme(plot.title = element_text(face="bold", size=16))

ggsave("outputs/1300/omy20-pcs-forward-only-hets.jpeg")

```


Hatchery fish, hatchery influenced fish, Eagle Lake fish.    


