---
title: "600-treemix"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Treemix

Giving this a go following a tutorial: https://speciationgenomics.github.io/Treemix/   

Require .clst file:    
.clst (cluster membership file)   

From plink, produced by --write-cluster. Valid input for --within.   

A text file with no header line, and one line per sample with the following three fields:

__1__    Family ID
__2__    Within-family ID
__3__    Cluster name

Made one of these "outputs/600/test5.clst". Some editiong of vcf2treemix.sh done. 10688 SNPs retained.

```{sh, eval=FALSE}
./600.1-vcf2treemix.sh outputs/600/test5-maf05p-sites-vcf.prune.vcf outputs/600/test5.clst
```

Now to loop through migration edges 0 to 5. There is a sample size flag "-noss"
```{sh, eval=FALSE}
for i in {0..5}
do
 treemix -i outputs/600/test5-maf05p-sites-vcf.prune.treemix.frq.gz -m $i -o outputs/600/test5.$i -root LCT -bootstrap -k 500 > outputs/600/test5.treemix_${i}_log &
done
```

With "-noss"
```{sh, eval=FALSE}
for i in {0..5}
do
 treemix -i outputs/600/test5-maf05p-sites-vcf.prune.treemix.frq.gz -m $i -o outputs/600/test5-noss.$i -root LCT -bootstrap -k 500 -noss> outputs/600/test5-noss.treemix_${i}_log &
done
```

## Plotting
```{r, warning=FALSE, message=FALSE}
library(RColorBrewer)
library(R.utils)
source("~/treemix/treemix-1.13/src/plotting_funcs.R")
prefix="outputs/600/test5"

par(mfrow=c(2,3))
for(edge in 0:5){
  plot_tree(cex=0.8,paste0(prefix,".",edge))
  title(paste(edge,"edges"))
}
```

## Plotting
```{r, warning=FALSE, message=FALSE}
prefix="outputs/600/test5-noss"

par(mfrow=c(2,3))
for(edge in 0:5){
  plot_tree(cex=0.8,paste0(prefix,".",edge))
  title(paste(edge,"edges"))
}
```


## More data!!!

Let's bring in more SNPs and individuals. 11,563 SNPs this way...

```{sh, eval=FALSE}
bcftools +prune -l 0.95 -w 10000 outputs/200/test5-maf05p-sites-vcf.sort.vcf.gz -Ov -o outputs/600/test5w10k.prune.vcf
./600.1-vcf2treemix.sh outputs/600/test5w10k.prune.vcf outputs/600/test5.clst

for i in {0..5}
do
 treemix -i outputs/600/test5w10k.prune.treemix.frq.gz -m $i -o outputs/600/test5w10k.$i -root LCT -bootstrap -k 500 -noss > outputs/600/test5w10k.treemix_${i}_log &
done
```

###Plotting More Data!!!!
Plotting
```{r, warning=FALSE, message=FALSE}
prefix="outputs/600/test5w10k"

par(mfrow=c(2,3))
for(edge in 0:5){
  plot_tree(cex=0.8,paste0(prefix,".",edge))
  title(paste(edge,"edges"))
}
```

#Test Dataset 4 
```{sh, eval=FALSE}
#Have to call the genotypes

angsd -P 3 -b bamlists/test4.bamlist -minInd 43  -out outputs/600/test4-maf05p-sites -minMaf 0.05 -minMapQ 30 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 -doGeno 4 -doPost 1 -postCutoff 0.95 -doVcf 1 -rf homoblocks/non-tetrasomic-non-inversion.txt > temp.out 2> temp.err

#Sort vcf
gunzip -c outputs/600//test4-maf05p-sites.vcf.gz | awk '$1 ~ /^#/ {print $0;next} {print $0 | "sort -k1,1 -k2,2n"}' > outputs/600/test4-maf05p-sites.sort.vcf
#Compress
bgzip outputs/600/test4-maf05p-sites.sort.vcf 
#Index
tabix outputs/600/test4-maf05p-sites.sort.vcf.gz
#Prune
bcftools +prune -l 0.9 -w 30000 outputs/600/test4-maf05p-sites.sort.vcf.gz -Ov -o outputs/600/test4-maf05p-sites.sort.prune.vcf

#Generate treemix files, first edit header of vcf, 26002 out of 26075 sites kept
./600.1-vcf2treemix.sh outputs/600/test4-maf05p-sites.sort.prune.vcf  outputs/600/test4.clst


for i in {0..5}
do
 treemix -i outputs/600/test4-maf05p-sites.sort.prune.treemix.frq.gz -m $i -o outputs/600/test4.$i -root LCT -bootstrap -k 500  > outputs/600/test4.treemix_${i}_log &
done
```

Plotting
```{r, warning=FALSE,message=FALSE}
prefix="outputs/600/test4"

par(mfrow=c(2,3))
for(edge in 0:5){
  plot_tree(cex=0.8,paste0(prefix,".",edge))
  title(paste(edge,"edges"))
}
```

