---
title: "800-phylonetworks"
author: "Mac Campbell"
date: "February 10, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# How to make a network?
I have been struggling to make a proper phylogenetic network from SNP data. That is, to construct a multispecies coalescent network model it just hasn't been happening.  

Olave and Meyer (2020) present a may to calculate concordance factors from a phylip formatted file for input into PhyloNetworks.  So, let's try that.

First I cloned https://github.com/melisaolave/SNPs2CF.
Required dependencies.    
install.packages("foreach")    
install.packages("doMC")     

```{r, warning=FALSE, message=FALSE}
source("~/github/SNPs2CF/functions.R")
```

```{r, warning=FALSE, message=FALSE, eval=FALSE}
#try the test data
output <- SNPs2CF(seqMatrix="~/github/SNPs2CF/examples/5taxa-30K_SNPs.phy", max.SNPs = 1000, bootstrap=FALSE, outputName="outputs/800/SNPs2CF_5taxa-1K_SNPs.csv", save.progress=FALSE);

#We can bootstrap the test data
outputbs <- SNPs2CF(seqMatrix="~/github/SNPs2CF/examples/5taxa-30K_SNPs.phy", max.SNPs = 1000, bootstrap=TRUE, outputName="outputs/800/SNPs2CF_5taxa-1K_SNPs-bootstrap.csv", save.progress=FALSE);

#We can also specify a multiple species/ind like so:
outputsp <- SNPs2CF(seqMatrix="~/github/SNPs2CF/examples/5taxa-2ind-30K_SNPs.phy", ImapName="~/github/SNPs2CF/examples/Imap.txt", between.sp.only = FALSE, max.SNPs = 50, bootstrap=FALSE, outputName="outputs/800/5taxa-2ind-1K_SNPs.phy-allQuart.csv", save.progress=FALSE);

```


For our data, let's choose a dataset that is representative, but, maybe small. Also need unlinked SNPs, but not necessarily corrected for asc bias in ML analysis, "test6-maf05p-sites.sort.prune.reheadered.min4.phy"

Test6.       

I need to make an Imap file. Done.    
Using all my snps and three cores. This will still take a hot minute.
```{r, warning=FALSE, message=FALE, eval=FALSE}
output <- SNPs2CF(seqMatrix="outputs/800/test6-maf05p-sites.sort.prune.reheadered.min4.phy",
                  ImapName="outputs/800/test6-imap.txt", between.sp.only = TRUE, max.SNPs = NULL,
                  bootstrap=FALSE, outputName="outputs/800/test6-AllSNP-btsp.csv",
                  save.progress=FALSE,
                  cores = 3);
```


#Credibility Intervals
To bootstrap I need to put together CF's with CIs

```{r, warning=FALSE, message=FALE, eval=FALSE}
ciout <- SNPs2CF(seqMatrix="outputs/800/test6-maf05p-sites.sort.prune.reheadered.min4.phy",
                  ImapName="outputs/800/test6-imap.txt", between.sp.only = TRUE, max.SNPs = NULL,
                  bootstrap=TRUE, boots.rep=1000,
                  outputName="outputs/800/test6-AllSNP-btsp-CI.csv",
                  save.progress=FALSE,
                  cores = 3);
```



