---
title: "902-hypothesis-testing"
author: "Mac Campbell"
date: "March 16, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

#Testing alternative hypotheses against consensus tree from IQ-TREE
Best-fit model: TVM+F+ASC+R2 chosen according to BIC

```{r}
library(tidyverse)
library(ggtree)
library(ape)
tree<-read.tree(file="outputs/900/test14-maf05p-sites.sort.prune.reheadered.min4.asc.phy.contree")
tree<-root(tree, c("PCT_PPP1_01","LCT_GACR_10"))
ggtree(tree)+geom_tiplab(size=2)+geom_nodelab()

```

Let's do some testing.    

__1__  Our unconstrained tree
```{sh, eval=FALSE}
iqtree -s example.phy -m TVM+F+ASC+R2 -st DNA --prefix example.unconstr
```

```{r}
tree<-read.tree(file="outputs/900/testing/example.unconstr.treefile")
tree<-root(tree, c("PCT_PPP1_01","LCT_GACR_10"))
ggtree(tree)+geom_tiplab(size=2)+geom_nodelab()

```

__2__ MRRT and Golden Trout Complex are sister
```{sh, eval=FALSE}
iqtree -s example.phy -m TVM+F+ASC+R2 -st DNA -g constrain1.tre --prefix example.constr1
```

```{r}
tree<-read.tree(file="outputs/900/testing/example.constr1.treefile")
tree<-root(tree, c("PCT_PPP1_01","LCT_GACR_10"))
ggtree(tree)+geom_tiplab(size=2)+geom_nodelab()
```

__3__ MRRT and redbands are monophyletic
```{sh, eval=FALSE}
iqtree -s example.phy -m TVM+F+ASC+R2 -st DNA -g constrain2.tre --prefix example.constr2 --redo
```

```{r}
tree<-read.tree(file="outputs/900/testing/example.constr2.treefile")
tree<-root(tree, c("PCT_PPP1_01","LCT_GACR_10"))
ggtree(tree)+geom_tiplab(size=2)+geom_nodelab()
```

__4__ MRRT and Coastal Rainbow Trout are monophyletic
```{sh, eval=FALSE}
iqtree -s example.phy -m TVM+F+ASC+R2 -st DNA -g constrain3.tre --prefix example.constr3 --redo
```

```{r}
tree<-read.tree(file="outputs/900/testing/example.constr3.treefile")
tree<-root(tree, c("PCT_PPP1_01","LCT_GACR_10"))
ggtree(tree)+geom_tiplab(size=2)+geom_nodelab()
```

# Now we combine our treefiles

```{sh, eval=FALSE}
cat example.unconstr.treefile ../test14-maf05p-sites.sort.reheadered.min4.asc.phy.contree example.constr1.treefile example.constr2.treefile example.constr3.treefile > example.treels

iqtree -s example.phy -z example.treels -te ../test14-maf05p-sites.sort.reheadered.min4.asc.phy.contree  -zb 10000 -zw -au -m TVM+F+ASC+R2 -st DNA -redo

#Also
#iqtree -s example.phy -z example.treels -n 0 -zb 10000 -zw -au -m TVM+F+ASC+R2 -st DNA -redo

```

Tree (1) unconstrained     
Tree (2) consensus tree   
Tree (3) constrained MRRT and CA Golden Trout Complex are monophyletic     
Tree (4) constrained redbands are monophyletic     
Tree (5) constrained MRRT+O.m.irideus are monophyletic      

    171   1 -26508.20531       0   0.631 +  0.733 +      1 +  0.733 +  0.959 +     0.629 +    0.851 +      
    172   2  -26541.6246  33.419  0.0832 +  0.104 +  0.173 +  0.104 +  0.167 +    0.0827 +    0.117 +     
    173   3 -26528.18073  19.975  0.0161 -  0.107 +  0.315 + 0.0644 +  0.171 +    0.0168 -   0.0528 +     
    174   4 -26516.46065  8.2553    0.23 +  0.267 +  0.623 +  0.267 +  0.633 +      0.23 +    0.422 +     
    175   5 -26523.39063  15.185  0.0405 + 0.0747 +  0.418 + 0.0747 +  0.203 +     0.042 +    0.125 +     
       
`iqtree -s example.phy -z example.treels -n 0 -zb 10000 -zw -au -m TVM+F+ASC+R2 -st DNA -redo`   

Using an initial parsimony tree to estimate model parameters instead of user supplied tree.    

    170   1 -26508.08365       0   0.632 +   0.73 +      1 +   0.73 +   0.96 +     0.629 +    0.855 +      
    171   2 -26541.67416  33.591  0.0836 +  0.102 +  0.169 +  0.102 +  0.165 +    0.0835 +     0.11 +     
    172   3 -26528.06953  19.986  0.0145 -  0.106 +  0.315 + 0.0649 +  0.174 +    0.0168 -   0.0599 +     
    173   4 -26516.38659  8.3029   0.227 +   0.27 +   0.63 +   0.27 +  0.638 +     0.227 +    0.425 +     
    174   5 -26523.28594  15.202  0.0433 + 0.0754 +  0.422 + 0.0754 +  0.207 +    0.0444 +    0.112 +     

Same results.    
#Wait, what happened?

Some evidence that MRRT and CA Golden Trout Complex are not monophyletic.      